### 2022-03-07 paper/fse22/approach.tex
approach

\Model generates input \sents with the following phases illustrated in
\ref{fig:OverallModel}: 1. search phase searches seed \sents according
to its \req of \lc, 2. seed parsing phase parses the found seed \sents
and extract their \cfg, 3. reference phase collects large corpus,
4. syntax expansion phase identifies structure for input augmentation,
and 5.\sent expansion phase generates natural expanded \sent. In this
section, we provide more details on each phase.

@@

\subsection{Reference phase}
In this phase, we take a large scale corpus as reference. We assume
that large corpus represents data distribution of real world,
the descripancy comparing seed sentence with the reference

structural information reference corpus is also parsed into \cfg.

\subsection{Syntax expansion phase}

\subsection{\Sent expansion phase}

>>>>

\Model generates input \sents with the following phases illustrated in
\ref{fig:OverallModel}: 1. search phase searches seed \sents according
to its \req of \lc, 2. seed parsing phase parses the found seed \sents
and extract their \cfg, 3. reference parsing phase collects \pcfg from
large corpus, 4. production differentiation phase identifies
structural expansion candidates for input expansion, and 5.\sent
selection phase generates natural expanded \sent. In this section, we
provide more details on each phase.

@@

\subsection{Reference parsing phase}
We take a large scale corpus as reference for seed expansion. It is
motivated by that large corpus represents data distribution of real
world, and the discrepancy between seed and reference leads to
determine how the seed can be expanded within real world data
distribution. This phase builds \pcfg from the reference corpus. \cfg
is constructed by parsing sentences in the corpus and extracting
production rules. In addition, the probability of \cfg is estimated by
its frequency over corpus. The outpus of this phase is the constructed
\pcfg, and it is compared with seed parse trees. For our
implementation, we build the \pcfg from the Penn Treebank corpus dataset.

\subsection{production differentiation phase}
Given the seed parse tree and reference \pcfg, \Model suggests
structural expansion candidates.

\subsection{\Sent selection phase}
